---
title: "  GBR Temperature Dashboard"
output:
  flexdashboard::flex_dashboard:
    logo: AIMS-NESP.png
    orientation: rows
    vertical_layout: scroll
    theme: cosmo
    social: [ "menu" ]
    navbar:
      - { title: "HOME", href: "https://eatlas.org.au/gbr/nesp-twq-4-2-temperature-data-2015-17", align: right }

params:
  siteID: 856
---

<!--
eklein. eklein@ocean-analytics.com.au
This is the code for generating the AIMS loggers Dashboard


-->


<style>
.navbar-inverse {
  background-color:#335b84;
  border-color:black;
}
.navbar-brand {
  font-size: x-large;
  color: white!important;
}
.nav-tabs-custom > .nav-tabs > li.active {border-top-color: #335b84}
}
</style>


```{r setup, include=FALSE}
library(flexdashboard)
library(htmltools)
library(leaflet)
library(plotly)
library(readr)
library(lubridate)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(DT)
library(stringr)


##############
## Constants
##############
summer.start = 274
climYear.start = 2015
climYear.end = 2017
siteID.selected = as.numeric(params$siteID)
##siteID.selected = 856     ## manual selection of a site


###############
## Functions
###############

tidyPlotly = function(pp){
  config(pp, displaylogo = FALSE)
  ## set xscale and fix legend labels
  pp = plotly_build(pp)
  #pp$x$layout$xaxis$tickvals = c(1,30,60,90,120,150,180,210,240,270,300, 330, 365)
  pp$x$layout$xaxis$tickvals = c(1, 32, 60, 91, 121, 152, 182, 213, 244, 274, 305, 335)
  pp$x$layout$xaxis$ticktext = c("OCT","NOV","DEC","JAN", "FEB","MAR","APR","MAY","JUN","JUL","AUG", "SEP", "OCT")

  ## dirty fix of the legend labels
  for (i in 1:length(pp$x$data)){
      if (!is.null(pp$x$data[[i]]$name)){
          pp$x$data[[i]]$name =  gsub("\\(","",str_split(pp$x$data[[i]]$name,",")[[1]][1])
      }
  }
  pp = pp %>% config(pp, displaylogo = FALSE)
  return(pp)
}


fillTimeGaps = function(df, interval){
  ## fill the time gaps with NAs
  df.time = data.frame(dateTime = seq(min(df$dateTime), max(df$dateTime), by=interval))
  df = full_join(df, df.time, by="dateTime")
  df = df %>% arrange(dateTime)
  return(df)
}


shiftSummer = function(dateTime, summer.start=274){
  ## shift yday relative summer start
  ## shift the year to match the climatological year start
  ## default Oct-01
  yDay.shifted = ifelse(yday(dateTime)<summer.start, yday(dateTime) + (365-summer.start) + 1, yday(dateTime) - summer.start + 1)
  year.shifted = ifelse(yday(dateTime)>=summer.start, year(dateTime)+1, year(dateTime))
  return(list(yDay.shifted= yDay.shifted, year.shifted = year.shifted))
}

shiftSummer.day = function(yDay, summer.start=274){
  ## shift yday relative summer start
  ## default Oct-01
  yDay.shifted = ifelse(yDay<summer.start, yDay + (365-summer.start) + 1, yDay - summer.start + 1)
  return(yDay.shifted)
}

addSmoothSD = function(climDF, spanNumber=0.5){
  ## add smoothed 1,2,3 sd bands to the climatology file
  ## based on summer yday
  climDF$sd1.upper = predict(loess((TEMP.mean+TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  climDF$sd1.lower = predict(loess((TEMP.mean-TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  climDF$sd2.upper = predict(loess((TEMP.mean+2*TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  climDF$sd2.lower = predict(loess((TEMP.mean-2*TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  climDF$sd3.upper = predict(loess((TEMP.mean+3*TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  climDF$sd3.lower = predict(loess((TEMP.mean-3*TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  return(climDF)
}


############
## SOURCES
## modify to your local settings
############
baseDir = "./data/temploggers/"
metadataDir = "./metadata/"
loggerDayDir = "./data/temploggers/bySite/Day"
loggerHourDir = "./data/temploggers/bySite/Hour"
climatologyDir = "./climatology/"
climatologySSTAARSDir = "./climatology/SSTAARS"
DHWDir = "./DHW/"


```


```{r readdata}
## read global metadata which is more complete
## I should change all to read this file instead
globalMD = suppressMessages(read_csv(file.path(metadataDir, "global_logger_METADATA.csv")))

siteId.list = globalMD$SITE_ID
if (!siteID.selected %in% siteId.list){
  stop(paste0(paste0(siteId.list, collapse = ","), "\nERROR: WRONG SITE ID. ---> ", siteID.selected))
}

globalMD = globalMD %>% filter(SITE_ID==siteID.selected)
globalMD$LATITUDE = round(globalMD$LATITUDE, 4)
globalMD$LONGITUDE = round(globalMD$LONGITUDE, 4)



## read day and hourly data
wtemp.hour = read_csv(file.path(loggerHourDir, globalMD$FILE_DATA))
wtemp.day = suppressMessages((read_csv(file.path(loggerDayDir, globalMD$FILE_DATA))))

## fix the name of the time variable
colnames(wtemp.day) = gsub("Day", "Time", colnames(wtemp.day))
colnames(wtemp.hour) = gsub("Hour", "Time", colnames(wtemp.hour))

## Fill time gaps
wtemp.hour = fillTimeGaps(wtemp.hour, "hours")
wtemp.day = fillTimeGaps(wtemp.day, "days")

## add day of the Year and day of the summer
summerDays = shiftSummer(wtemp.hour$dateTime)
wtemp.hour$yDay = yday(wtemp.hour$dateTime)
wtemp.hour$yDay.summer = summerDays$yDay.shifted
wtemp.hour$year.summer = summerDays$year.shifted

summerDays = shiftSummer(wtemp.day$dateTime)
wtemp.day$yDay = yday(wtemp.day$dateTime)
wtemp.day$yDay.summer = summerDays$yDay.shifted
wtemp.day$year.summer = summerDays$year.shifted

## filter by location and dates
wtemp.hour.FL.full = wtemp.hour %>% filter(SLFL=="FL")
wtemp.hour.SL.full = wtemp.hour %>% filter(SLFL=="SL")
wtemp.day.FL.full = wtemp.day %>% filter(SLFL=="FL")
wtemp.day.SL.full = wtemp.day %>% filter(SLFL=="SL")


wtemp.hour.SL = wtemp.hour %>% filter(SLFL=="SL", year.summer>=climYear.start, year.summer<=climYear.end)
wtemp.hour.FL = wtemp.hour %>% filter(SLFL=="FL", year.summer>=climYear.start, year.summer<=climYear.end)
wtemp.day.SL = wtemp.day %>% filter(SLFL=="SL", year.summer>=climYear.start, year.summer<=climYear.end)
wtemp.day.FL = wtemp.day %>% filter(SLFL=="FL", year.summer>=climYear.start, year.summer<=climYear.end)

## read loggers climatology if available


climMetadata = suppressMessages(read_csv(file.path(climatologyDir, "climatology_METADATA.csv")))
climMetadata.selected = climMetadata[climMetadata$SITE_ID==siteID.selected, c("SITE_ID", "SLFL", "fileName")]
availLocs = unique(climMetadata.selected$SLFL)
if (globalMD$CLIM_FLAT){
  climFL = suppressMessages(read_csv(file.path(climatologyDir, globalMD$FILE_CLIM_FLAT)))
  climFL = addSmoothSD(climFL)
}
if (globalMD$CLIM_SLOPE){
  climSL = suppressMessages(read_csv(file.path(climatologyDir, globalMD$FILE_CLIM_SLOPE)))
  climSL = addSmoothSD(climSL)
}


## get SSTAARS climatology
climSSTAARSmetadata = suppressMessages(read_csv(file.path(climatologySSTAARSDir, "loggers_climatology_SSTAARS_METADATA.csv")))
SSTAARS.fileName = climSSTAARSmetadata$climFileName[climSSTAARSmetadata$SITE_ID==siteID.selected]
climSSTAARS = suppressMessages(read_csv(file.path(climatologySSTAARSDir, SSTAARS.fileName)))
climSSTAARS$yDay.summer = shiftSummer.day(climSSTAARS$yDay)



## get min/max temp for plot scales. Add 2 deg to be safe
Temp.scale.min = floor(min(min(wtemp.hour.FL$TEMP, na.rm=T),
                           min(wtemp.hour.SL$TEMP, na.rm=T),
                           min(climSSTAARS$TEMP), na.rm=T)) - 2

Temp.scale.max = ceiling(max(max(wtemp.hour.FL$TEMP, na.rm=T),
                           max(wtemp.hour.SL$TEMP, na.rm=T),
                           max(climSSTAARS$TEMP),na.rm=T)) + 2

## if loggers clim exists, consider sd band for plot limits
if (globalMD$CLIM_SLOPE){
  Temp.scale.min = floor(min(Temp.scale.min, min(climSL$sd2.lower, na.rm=T)))
  Temp.scale.max = ceiling(max(Temp.scale.max, min(climSL$sd2.upper, na.rm=T)))
}
if (globalMD$CLIM_FLAT){
  Temp.scale.min = floor(min(Temp.scale.min, min(climFL$sd2.lower, na.rm=T)))
  Temp.scale.max = ceiling(max(Temp.scale.max, min(climFL$sd2.upper, na.rm=T)))
}

## get DHW and MMM
DHW = suppressMessages(read_csv(file.path(DHWDir, "LoggerSITE_MMM.csv")))
DHW = DHW %>% filter(SITE_ID==siteID.selected)


```




CLIMATOLOGY
=====================================

Row (data-hight=300)
-------------------------------------

### Location

```{r}

loclatlon = as.character(str_split(globalMD$LOCLATLON_PAIRS, ", ", simplify = T))
locationDF = data.frame(Location = str_split(loclatlon, "\\|", simplify = T)[,1],
                        Latitude = as.numeric(str_split(loclatlon, "\\|", simplify = T)[,2]),
                        Longitude = as.numeric(str_split(loclatlon, "\\|", simplify = T)[,3]))

lat.mean = mean(locationDF$Latitude, na.rm=T)
lon.mean = mean(locationDF$Longitude, na.rm=T)
siteName = globalMD$SITE

m = leaflet(locationDF) %>%
  addProviderTiles(providers$Esri.WorldImagery) %>% setView(lng = lon.mean, lat = lat.mean, zoom = 11) %>%
  addCircleMarkers(lat=~Latitude, lng=~Longitude, label = ~Location,
                   radius = 8, fillColor = "#791e89", fillOpacity = 0.7, color = "white", weight = 2,
                   clusterOptions = markerClusterOptions())
m
```


### Basic statistics of the Time Series


```{r}
### make summary statistics table
statTable = data.frame(Item = character(),
                       Value = character(),
                       stringsAsFactors = FALSE)

## get the max TEMP.q95
tempq95.max = max(wtemp.day$TEMP.q95, ma.rm=T)
Tempsummer.maxmean = quantile(wtemp.day$TEMP[wtemp.day$yDay<=120], 0.95, na.rm=T)

Item = gsub("_", " ", colnames(globalMD)[c(1:9, 11:12)])
Item = c(Item, c("Historical summer TEMP (p95%)", "2016 summer max TEMP", "2017 summer max TEMP",
                 "NOAA's MMM", "NOAA's DHW max 2016", "NOAA's DHWmax 2017"))
Value = as.character(globalMD[c(1:9, 11:12)])
Value = as.character(c(globalMD[1:5], as.character(globalMD$DATE_START), as.character(globalMD$DATE_END), globalMD[c(8:9,11:12)],
          round(Tempsummer.maxmean, 2),  # max TEMP
          round(max(wtemp.day$TEMP.max[year(wtemp.day$dateTime)==2016 & wtemp.day$yDay<=120], na.rm=T), 2),     # 2016 maTEMP
          round(max(wtemp.day$TEMP.max[year(wtemp.day$dateTime)==2017 & wtemp.day$yDay<=120], na.rm=T), 2),     # 2016 maTEMP
          round(DHW$MMM,2),
          round(DHW$DHWmax2016,2),
          round(DHW$DHWmax2017,2)))


statsTable = data.frame(Item, Value, stringsAsFactors = FALSE)

DT::datatable(statsTable, colnames=c("", ""), caption = tags$h2(globalMD$SITE),
              options = list(pageLength = 6, dom = 'tip'), rownames = FALSE, fillContainer = T)


```



### Description

Mass coral bleaching has occurred on the Great Barrier Reef (GBR) in 2016 and 2017 as part of global bleaching event that started in late 2014 (NOAA). The combined effect has meant that more area of the reefs throughout the GBR have bleached to some degree of severity, depending the duration and extreme temperature stress above the historical summer maximum temperature for each location.

Go back to

[Drivers of Bleaching on the Great Barrier Reef - Compilation of temperature data from 2015, 2016 2017](https://eatlas.org.au/gbr/nesp-twq-4-2-temperature-data-2015-17)



Row
-------------------------------------

### Historical summer mean Temperature

```{r}
valueBox(value=round(mean(wtemp.day$TEMP[wtemp.day$yDay<=120], na.rm=T) ,1), icon="fa-thermometer-half", color = "#335b84")
```

### Historial summer Maximum 95% percentile

```{r}
#hist.max.date = wtemp.day$dateTime[which.max(wtemp.day$TEMP.q95)]
Tempsummer.maxmean = round(quantile(wtemp.day$TEMP[wtemp.day$yDay<=120], 0.95, na.rm=T), 1)
valueBox(value = Tempsummer.maxmean, icon = "fa-thermometer-three-quarters", color = "#335b84")
```

### Climatological summer max (SSTAARS)

```{r}
clim.summer.max = round(max(climSSTAARS$TEMP[climSSTAARS$yDay<=120]),1)
valueBox(value=clim.summer.max, icon="fa-thermometer-three-quarters", color = "#335b84")
```

### Climatological summer mean (SSTAARS)

```{r}
clim.summer.mean = round(mean(climSSTAARS$TEMP[climSSTAARS$yDay<=120]), 1)
valueBox(value=clim.summer.mean, icon="fa-thermometer-half", color = "#335b84")
```

### 2016: Days above summer max

```{r}
daysBelowMean = sum(climSSTAARS$TEMP[climSSTAARS$yDay<=120]<mean(climSSTAARS$TEMP[climSSTAARS$yDay<=120]))
daysAboveMean = sum(climSSTAARS$TEMP[climSSTAARS$yDay<=120]>=mean(climSSTAARS$TEMP[climSSTAARS$yDay<=120]))
days2016 = wtemp.day %>% filter(year.summer==2016) %>% group_by(yDay.summer) %>%
  summarise(TEMP = mean(TEMP, na.rm=T))

daysAboveMax.2016 = sum(days2016$TEMP > clim.summer.max, na.rm=T)
gauge(value = daysAboveMax.2016, min = 0, max = 120,
      gaugeSectors(success = c(0, daysBelowMean), danger = c(daysBelowMean+1, daysAboveMean)))

```

### 2017: Days above summer max

```{r}
days2017 = wtemp.day %>% filter(year.summer==2017) %>% group_by(yDay.summer) %>%
  summarise(TEMP = mean(TEMP, na.rm=T))

daysAboveMax.2017 = sum(days2017$TEMP > clim.summer.max, na.rm=T)
gauge(value = daysAboveMax.2017, min = 0, max = 120,
      gaugeSectors(success = c(0, daysBelowMean), danger = c(daysBelowMean+1, daysAboveMean)))

```



Row {.tabset}
---------------------------------------

> 2016/2017

### Reef FLAT

```{r plotconst}
yearsToPlot = c(2015, 2016, 2017)
colorValues = c( "steelblue", "#fc8d59", "#d73027")
colorLabels = c("2014-2015", "2015-2016", "2016-2017")

```

```{r}
seriesColor.labels = character()
seriesColor.values = character()
yearsAvailable = unique(wtemp.day.FL$year.summer)

if (length(yearsAvailable)==0){
  ## no data available
  seriesColor.labels = c(seriesColor.labels, "SSTAARS Clim")
  seriesColor.values = c(seriesColor.values, "blue4")

  pp = ggplot()
  pp = pp + geom_line(data=climSSTAARS, aes(yDay.summer, TEMP, colour="SSTAARS Clim")) +
    annotate("text", x = 200, y = (Temp.scale.min + Temp.scale.max)/2, label = "NO LOGGER DATA AVAILABLE FOR 2015-2017")
} else {
  pp = ggplot()
  if (globalMD$CLIM_FLAT){
    pp = pp +
      geom_ribbon(data = climFL, aes(x=yDay.summer, ymin = sd1.lower, ymax = sd1.upper, fill= "1sd"), alpha=0.3) +
      geom_ribbon(data = climFL, aes(x=yDay.summer, ymin = sd2.lower, ymax = sd2.upper, fill= "2sd"), alpha=0.05) +
      geom_line(data = climFL, aes(x=yDay.summer, y=TEMP.mean, colour="Logger Clim")) +
      scale_color_manual(values = c("grey50", "grey10") , labels = c("1sd","2sd"), aesthetics = "fill")
      seriesColor.labels = c(seriesColor.labels, "Logger Clim")
      seriesColor.values = c(seriesColor.values, "steelblue")

  }
  ## add SSTAARS climatology
  pp = pp + geom_line(data=climSSTAARS, aes(yDay.summer, TEMP, colour="SSTAARS Clim"))
  seriesColor.labels = c(seriesColor.labels, "SSTAARS Clim")
  seriesColor.values = c(seriesColor.values, "blue4")

  ## add series
  if (2015 %in% yearsAvailable){
    pp = pp + geom_line(data = wtemp.day.FL %>% filter(year.summer==2015), aes(yDay.summer, TEMP, colour="2014-2015"), size=1, alpha=0.7)
      seriesColor.labels = c(seriesColor.labels, "2015")
      seriesColor.values = c(seriesColor.values, "steelblue")
  }
  if (2016 %in% yearsAvailable){
    pp = pp + geom_line(data = wtemp.day.FL %>% filter(year.summer==2016), aes(yDay.summer, TEMP, colour="2015-2016"), size=1, alpha=0.7)
    seriesColor.labels = c(seriesColor.labels, "2016")
    seriesColor.values = c(seriesColor.values, "#fc8d59")
  }
  if (2017 %in% yearsAvailable){
    pp = pp + geom_line(data = wtemp.day.FL %>% filter(year.summer==2017), aes(yDay.summer, TEMP, colour="2016-2017"), size=1, alpha=0.7)
    seriesColor.labels = c(seriesColor.labels, "2017")
    seriesColor.values = c(seriesColor.values, "#d73027")
  }
}
## layout
pp = pp + labs(x="", y="Temperature 째C") +
  ylim(Temp.scale.min, Temp.scale.max) +
  scale_color_manual(values = rev(seriesColor.values),
                     labels = rev(seriesColor.labels), aesthetics = "color") +
  theme_pubclean() +
  theme(legend.title = element_blank())
pp = ggplotly(pp)
pp = tidyPlotly(pp)
pp

```


### Reef SLOPE

```{r}
yearsToPlot = c(2015, 2016, 2017)
colorValues = c( "steelblue", "#fc8d59", "#d73027")
colorLabels = c("2014-2015", "2015-2016", "2016-2017")

```

```{r}
seriesColor.labels = character()
seriesColor.values = character()
yearsAvailable = unique(wtemp.day.SL$year.summer)

if (length(yearsAvailable)==0){
  ## no data available
  seriesColor.labels = c(seriesColor.labels, "SSTAARS Clim")
  seriesColor.values = c(seriesColor.values, "blue4")

  pp = ggplot()
  pp = pp + geom_line(data=climSSTAARS, aes(yDay.summer, TEMP, colour="SSTAARS Clim")) +
    annotate("text", x = 200, y = (Temp.scale.min + Temp.scale.max)/2, label = "NO LOGGER DATA AVAILABLE FOR 2015-2017")
} else {
  pp = ggplot()
  if (globalMD$CLIM_SLOPE){
    pp = pp +
      geom_ribbon(data = climSL, aes(x=yDay.summer, ymin = sd1.lower, ymax = sd1.upper, fill= "1sd"), alpha=0.3) +
      geom_ribbon(data = climSL, aes(x=yDay.summer, ymin = sd2.lower, ymax = sd2.upper, fill= "2sd"), alpha=0.05) +
      geom_line(data = climSL, aes(x=yDay.summer, y=TEMP.mean, colour="Logger Clim")) +
      scale_color_manual(values = c("grey50", "grey10") , labels = c("1sd","2sd"), aesthetics = "fill")
      seriesColor.labels = c(seriesColor.labels, "Logger Clim")
      seriesColor.values = c(seriesColor.values, "steelblue")

  }
  ## add SSTAARS climatology
  pp = pp + geom_line(data=climSSTAARS, aes(yDay.summer, TEMP, colour="SSTAARS Clim"))
  seriesColor.labels = c(seriesColor.labels, "SSTAARS Clim")
  seriesColor.values = c(seriesColor.values, "blue4")

  ## add series
  if (2015 %in% yearsAvailable){
    pp = pp + geom_line(data = wtemp.day.SL %>% filter(year.summer==2015), aes(yDay.summer, TEMP, colour="2014-2015"), size=1, alpha=0.7)
      seriesColor.labels = c(seriesColor.labels, "2015")
      seriesColor.values = c(seriesColor.values, "steelblue")
  }
  if (2016 %in% yearsAvailable){
    pp = pp + geom_line(data = wtemp.day.SL %>% filter(year.summer==2016), aes(yDay.summer, TEMP, colour="2015-2016"), size=1, alpha=0.7)
    seriesColor.labels = c(seriesColor.labels, "2016")
    seriesColor.values = c(seriesColor.values, "#fc8d59")
  }
  if (2017 %in% yearsAvailable){
    pp = pp + geom_line(data = wtemp.day.SL %>% filter(year.summer==2017), aes(yDay.summer, TEMP, colour="2016-2017"), size=1, alpha=0.7)
    seriesColor.labels = c(seriesColor.labels, "2017")
    seriesColor.values = c(seriesColor.values, "#d73027")
  }
}
## layout
pp = pp + labs(x="", y="Temperature 째C") +
  ylim(Temp.scale.min, Temp.scale.max) +
  scale_color_manual(values = rev(seriesColor.values),
                     labels = rev(seriesColor.labels), aesthetics = "color") +
  theme_pubclean() +
  theme(legend.title = element_blank())
pp = ggplotly(pp)
pp = tidyPlotly(pp)
pp

```


Row
----------------------------------------

### Notes

The time series corresponding to 2015, 2016 and 2017, when available, are plotted in its climatological year, starting at October 1st  of the previous year and ending September 30 of its year. For example, the 2016 time series starts at 2015-10-01 and ends 2016-09-30.

The default climatology is the one extracted for the site's coordinates from the SST Atlas of Australian Regional Seas (SSTAARS) (see [Wijffels et al. 2018](http://epubs.aims.gov.au/handle/11068/14860)), at a spatial resolution of ~2km. When at least ten years of data were available, a climatology was derived from temperature loggers records for the reef flat and/or reef slope. In this case, one and two standard deviation bands are ploted as reference (grey bands).

The maximun temperature reported in the value Box is the maximum value of the 95% percentile of the day. This quantile avoids the effect of over-heating in some loggers located in the reef flat due to an occasional exposure to the air.





TIME SERIES
=========================================

Row
-----------------------------------------


### Reef FLAT

```{r}

fig = plot_ly(x=~wtemp.hour.FL.full$dateTime, y=~wtemp.hour.FL.full$TEMP, mode='lines', type="scatter",
              line = list(color = "coral"), name = "Hourly") %>%
  add_trace(x = ~wtemp.day.FL.full$dateTime, y= ~wtemp.day.FL.full$TEMP, type="scatter", mode="lines",
            line = list(color = "red"), name = "Day mean") %>%
  layout(xaxis = list(title=""), yaxis = list(title = "Temperature (째C)")) %>%
  rangeslider(start=ymd(20161001), end = ymd(20170930))
fig = fig %>% config(pp, displaylogo = FALSE)

fig

```

Row
-------------------------------------------

### Reef SLOPE

```{r}
fig = plot_ly(x=~wtemp.hour.SL.full$dateTime, y=~wtemp.hour.SL.full$TEMP, mode='lines', type="scatter",
                  line = list(color = "steelblue"), name = "Hourly", connectgaps=FALSE) %>%
  add_trace(x = ~wtemp.day.SL.full$dateTime, y= ~wtemp.day.SL.full$TEMP, type="scatter", mode="lines",
            line = list(color = "blue"), name = "Day mean", connectgaps=FALSE) %>%
  layout(xaxis = list(title=""), yaxis = list(title = "Temperature (째C)")) %>%
  rangeslider(start=ymd(20161001), end = ymd(20170430))
fig = fig %>% config(pp, displaylogo = FALSE)

fig

```


Row
------------------------------------------------

#### Notes

The times series represents all available records up to `r floor_date(globalMD$DATE_END, "day")`. For more details go to the [AIMS logger program](http://maps.aims.gov.au/index.html?intro=false&z=4&ll=142.91883,-17.51872&l0=aims_aims:AIMS - Temperature Loggers,ea_World_NE2-coast-cities-reefs_Baselayer)



