---
title: "  GBR Temperature Dashboard"
output:
  flexdashboard::flex_dashboard:
    logo: AIMS-NESP.png
    orientation: rows
    vertical_layout: scroll
    theme: cosmo
    social: [ "menu" ]
    navbar:
      - { title: "HOME", href: "https://eatlas.org.au/gbr/nesp-twq-4-2-temperature-data-2015-17", align: right }
params:
  siteID: 30004
---

<!--
eklein. eklein@ocean-analytics.com.au
This is the code for generating the QLD-wavebuoys Dashboard


-->


<style>
.navbar-inverse {
  background-color:#335b84;
  border-color:black;
}
.navbar-brand {
  font-size: x-large;
  color: white!important;
}
.nav-tabs-custom > .nav-tabs > li.active {border-top-color: #335b84}
}
</style>


```{r setup, include=FALSE}
library(flexdashboard)
library(htmltools)
library(leaflet)
library(plotly)
library(readr)
library(lubridate)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(DT)
library(stringr)
library(R.utils)


##############
## Constants
##############
summer.start = 274
climYear.start = 2015
climYear.end = 2017
siteID.selected = as.numeric(params$siteID)
##siteID.selected = 30002     ## manual selection of a site


###############
## Functions
###############

tidyPlotly = function(pp){
  config(pp, displaylogo = FALSE)
  ## set xscale and fix legend labels
  pp = plotly_build(pp)
  #pp$x$layout$xaxis$tickvals = c(1,30,60,90,120,150,180,210,240,270,300, 330, 365)
  pp$x$layout$xaxis$tickvals = c(1, 32, 60, 91, 121, 152, 182, 213, 244, 274, 305, 335)
  pp$x$layout$xaxis$ticktext = c("OCT","NOV","DEC","JAN", "FEB","MAR","APR","MAY","JUN","JUL","AUG", "SEP", "OCT")

  ## dirty fix of the legend labels
  for (i in 1:length(pp$x$data)){
      if (!is.null(pp$x$data[[i]]$name)){
          pp$x$data[[i]]$name =  gsub("\\(","",str_split(pp$x$data[[i]]$name,",")[[1]][1])
      }
  }
  pp = pp %>% config(pp, displaylogo = FALSE)
  return(pp)
}


fillTimeGaps = function(df, interval){
  ## fill the time gaps with NAs
  df.time = data.frame(dateTime = seq(min(df$dateTime), max(df$dateTime), by=interval))
  df = full_join(df, df.time, by="dateTime")
  df = df %>% arrange(dateTime)
  return(df)
}


shiftSummer = function(dateTime, summer.start=274){
  ## shift yday relative summer start
  ## shift the year to match the climatological year start
  ## default Oct-01
  yDay.shifted = ifelse(yday(dateTime)<summer.start, yday(dateTime) + (365-summer.start) + 1, yday(dateTime) - summer.start + 1)
  year.shifted = ifelse(yday(dateTime)>=summer.start, year(dateTime)+1, year(dateTime))
  return(list(yDay.shifted= yDay.shifted, year.shifted = year.shifted))
}

shiftSummer.day = function(yDay, summer.start=274){
  ## shift yday relative summer start
  ## default Oct-01
  yDay.shifted = ifelse(yDay<summer.start, yDay + (365-summer.start) + 1, yDay - summer.start + 1)
  return(yDay.shifted)
}

addSmoothSD = function(climDF, spanNumber=0.5){
  ## add smoothed 1,2,3 sd bands to the climatology file
  ## based on summer yday
  climDF$sd1.upper = predict(loess((TEMP.mean+TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  climDF$sd1.lower = predict(loess((TEMP.mean-TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  climDF$sd2.upper = predict(loess((TEMP.mean+2*TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  climDF$sd2.lower = predict(loess((TEMP.mean-2*TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  climDF$sd3.upper = predict(loess((TEMP.mean+3*TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  climDF$sd3.lower = predict(loess((TEMP.mean-3*TEMP.sd)~yDay.summer, data=climDF, span=spanNumber), climDF$yDay.summer)
  return(climDF)
}


############
## SOURCES
## modify to your local settings
############
baseDir = "./data/wavebuoys/"
metadataDir = "./metadata/"
loggerDayDir = "./data/wavebuoys/bySite/Day"
loggerHourDir = "./data/wavebuoys/bySite/Hour"
climatologyDir = "./climatology/"
climatologySSTAARSDir = "./climatology/SSTAARS"
DHWDir = "./DHW/"


```


```{r readdata}
## read global metadata which is more complete
## I should change all to read this file instead
globalMD = suppressMessages(read_csv(file.path(baseDir, "global_waveriders_METADATA.csv")))

siteId.list = globalMD$SITE_ID
if (!siteID.selected %in% siteId.list){
  stop(paste0(paste0(siteId.list, collapse = ","), "\nERROR: WRONG SITE ID. ---> ", siteID.selected))
}

globalMD = globalMD %>% filter(SITE_ID==siteID.selected)
globalMD$LATITUDE = round(globalMD$LATITUDE, 4)
globalMD$LONGITUDE = round(globalMD$LONGITUDE, 4)

## read day and hourly data
wtemp.hour = suppressMessages((read_csv(file.path(loggerHourDir, globalMD$FILE_DATA), col_types = "icTnnnnnn")))
wtemp.day = suppressMessages((read_csv(file.path(loggerDayDir, globalMD$FILE_DATA), col_types = "icTnnnnnnnn")))

## fix the name of the time variable
colnames(wtemp.day) = gsub("Day", "Time", colnames(wtemp.day))
colnames(wtemp.hour) = gsub("Hour", "Time", colnames(wtemp.hour))

## Fill time gaps
wtemp.hour = wtemp.hour %>% filter(!is.na(dateTime)) %>%
  arrange(dateTime) %>% fillTimeGaps(interval = "hours")
wtemp.day = wtemp.day %>% filter(!is.na(dateTime)) %>%
  arrange(dateTime) %>% fillTimeGaps(interval = "days")

## add day of the Year and day of the summer
summerDays = shiftSummer(wtemp.hour$dateTime)
wtemp.hour$yDay = yday(wtemp.hour$dateTime)
wtemp.hour$yDay.summer = summerDays$yDay.shifted
wtemp.hour$year.summer = summerDays$year.shifted

summerDays = shiftSummer(wtemp.day$dateTime)
wtemp.day$yDay = yday(wtemp.day$dateTime)
wtemp.day$yDay.summer = summerDays$yDay.shifted
wtemp.day$year.summer = summerDays$year.shifted


## get SSTAARS climatology
climSSTAARSmetadata = suppressMessages(read_csv(file.path(climatologySSTAARSDir, "waveriders_climatology_SSTAARS_METADATA.csv")))
SSTAARS.fileName = climSSTAARSmetadata$climFileName[climSSTAARSmetadata$SITE_ID==siteID.selected]
climSSTAARS = suppressMessages(read_csv(file.path(climatologySSTAARSDir, SSTAARS.fileName)))
climSSTAARS$yDay.summer = shiftSummer.day(climSSTAARS$yDay)



## get min/max temp for plot scales. Add 2 deg to be safe
Temp.scale.min = floor(min(min(wtemp.hour$TEMP, na.rm=T),
                           min(climSSTAARS$TEMP), na.rm=T)) - 2

Temp.scale.max = ceiling(max(max(wtemp.hour$TEMP, na.rm=T),
                          max(climSSTAARS$TEMP),na.rm=T)) + 2

## get DHW and MMM
DHW = suppressMessages(read_csv(file.path(DHWDir, "WaveRiderSITE_MMM.csv")))
DHW = DHW %>% filter(SITE_ID==siteID.selected)


```




CLIMATOLOGY
=====================================

Row (data-hight=300)
-------------------------------------

### Location

```{r}

## read map QLD_towns
QLDtowns = read.csv(file.path(metadataDir, "QLD_towns.csv"))

lat.mean = globalMD$LATITUDE
lon.mean = globalMD$LONGITUDE
siteName = globalMD$SITE

m = leaflet() %>%
  addProviderTiles(providers$Esri.WorldImagery) %>% setView(lng = lon.mean, lat = lat.mean, zoom = 8) %>%
  addCircleMarkers(lat=lat.mean, lng=lon.mean, label = siteName,
                   radius = 8, fillColor = "#791e89", fillOpacity = 0.7, color = "white", weight = 2) %>%
    addCircleMarkers(data=QLDtowns, lat = ~lat, lng = ~lng, label = ~NAME,
                   labelOptions = labelOptions(noHide = T, textOnly = TRUE, style= list(color="white", "font-size" = "12px")),
                   radius = 4, fillColor = "black", fillOpacity = 0.7, color = "white", weight = 1)

m
```


### Basic statistics of the Time Series


```{r}
### make summary statistics table
## get the max TEMP.q95
tempq95.summer.max = round(quantile(wtemp.hour$TEMP[wtemp.hour$yDay<=120], 0.95, na.rm=T), 2)
tempmax.summer.2016 = round(max(wtemp.hour$TEMP[wtemp.hour$yDay<=120 & year(wtemp.hour$dateTime)==2016], na.rm=T), 2)
tempmax.summer.2017 = round(max(wtemp.hour$TEMP[wtemp.hour$yDay<=120 & year(wtemp.hour$dateTime)==2017], na.rm=T), 2)
Tempsummer.maxmean = quantile(wtemp.hour$TEMP[wtemp.hour$yDay<=120], 0.95, na.rm=T)
availableYears = seqToHumanReadable(paste0(unique(year(wtemp.day$dateTime), collapse=",")))
availableDepths = globalMD$NOMINAL_DEPTH_AVAILABLE

tableList = list(c("SITE", globalMD$SITE),
                 c("TYPE", "WAVEBUOY"),
                 c("Longitude (E)", as.character(round(globalMD$LONGITUDE, 4))),
                 c("Latitude (N)", as.character(round(globalMD$LATITUDE, 4))),
                 c("START date", as.character(globalMD$DATE_START)),
                 c("END date", as.character(globalMD$DATE_END)),
                 c("Available Years", availableYears),
                 c("Water Depth (m)", availableDepths),
                 c("Historical summer TEMP (p95%) (°C)", as.character(tempq95.summer.max)),
                 c("2016 summer max TEMP (°C)", as.character(tempmax.summer.2016)),
                 c("2017 summer max TEMP (°C)", as.character(tempmax.summer.2017)),
                 c("NOAAs MMM (°C)", round(DHW$MMM, 2)),
                 c("2016 NOAAs max DHW (degrees-week)", round(DHW$DHWmax2016, 2)),
                 c("2017 NOAAs max DHW (degrees-week)", round(DHW$DHWmax2017, 2)))


statsTable = data.frame(Item = character(),
                        Value = character(),
                        stringsAsFactors = FALSE)
for (item in 1: length(tableList)){
  statsTable = bind_rows(statsTable,
                         data.frame(Item = tableList[[item]][[1]],
                                    Value = tableList[[item]][[2]],
                                    stringsAsFactors = FALSE))
}

DT::datatable(statsTable, colnames=c("", ""), caption = tags$h2(paste0(globalMD$SITE, " -- Wave Buoy")),
              options = list(pageLength = 6, dom = 'tip'), rownames = FALSE, fillContainer = T, style = "bootstrap")


```





### Description


Mass coral bleaching has occurred on the Great Barrier Reef (GBR) in 2016 and 2017 as part of global bleaching event that started in late 2014 and lasted until late 2017 (NOAA).  This has meant large areas  of coral throughout the GBR have bleached to some degree of severity, depending the duration and extreme temperature stress above the historical summer maximum temperature for each location. This collection seeks to provide a central location from which publicly available temperature records can be viewed and downloaded.

The Queensland Government maintain a network of coastal wave monitoring sites to measure the height and direction of waves along the Queensland coast. The wave buoys also register temperature at the depth of the instrument.

For more details go to [Queensland Government Wave Monitoring site](https://www.qld.gov.au/environment/coasts-waterways/beach/monitoring)


Data source:  [Wave Monitoring Data site](https://www.qld.gov.au/environment/coasts-waterways/beach/monitoring/waves-sites)


Go back to

[Drivers of Bleaching on the Great Barrier Reef - Compilation of temperature data from 2015-2017](https://eatlas.org.au/gbr/nesp-twq-4-2-temperature-data-2015-17)


Row
-------------------------------------

### Historical summer mean Temperature

```{r}
valueBox(value=round(mean(wtemp.day$TEMP[wtemp.day$yDay<=120], na.rm=T) ,1), icon="fa-thermometer-half", color = "#335b84")
```

### Historial summer Maximum 95% percentile

```{r}
#hist.max.date = wtemp.day$dateTime[which.max(wtemp.day$TEMP.q95)]
Tempsummer.maxmean = round(quantile(wtemp.day$TEMP[wtemp.day$yDay<=120], 0.95, na.rm=T), 1)
valueBox(value = Tempsummer.maxmean, icon = "fa-thermometer-three-quarters", color = "#335b84")
```

### Climatological summer max (SSTAARS)

```{r}
clim.summer.max = round(max(climSSTAARS$TEMP[climSSTAARS$yDay<=120]),1)
valueBox(value=clim.summer.max, icon="fa-thermometer-three-quarters", color = "#335b84")
```

### Climatological summer mean (SSTAARS)

```{r}
clim.summer.mean = round(mean(climSSTAARS$TEMP[climSSTAARS$yDay<=120]), 1)
valueBox(value=clim.summer.mean, icon="fa-thermometer-half", color = "#335b84")
```

### 2016: Days above summer max

```{r}
daysBelowMean = sum(climSSTAARS$TEMP[climSSTAARS$yDay<=120]<mean(climSSTAARS$TEMP[climSSTAARS$yDay<=120]))
daysAboveMean = sum(climSSTAARS$TEMP[climSSTAARS$yDay<=120]>=mean(climSSTAARS$TEMP[climSSTAARS$yDay<=120]))
days2016 = wtemp.day %>% filter(year.summer==2016) %>% group_by(yDay.summer) %>%
  summarise(TEMP = mean(TEMP, na.rm=T))

daysAboveMax.2016 = sum(days2016$TEMP > clim.summer.max, na.rm=T)
gauge(value = daysAboveMax.2016, min = 0, max = 120,
      gaugeSectors(success = c(0, daysBelowMean), danger = c(daysBelowMean+1, daysAboveMean)))

```

### 2017: Days above summer max

```{r}
days2017 = wtemp.day %>% filter(year.summer==2017) %>% group_by(yDay.summer) %>%
  summarise(TEMP = mean(TEMP, na.rm=T))

daysAboveMax.2017 = sum(days2017$TEMP > clim.summer.max, na.rm=T)
gauge(value = daysAboveMax.2017, min = 0, max = 120,
      gaugeSectors(success = c(0, daysBelowMean), danger = c(daysBelowMean+1, daysAboveMean)))

```





Row
---------------------------------------

### 2016/2017


```{r plotconst}
yearsToPlot = c(2015, 2016, 2017)
colorValues = c( "steelblue", "#fc8d59", "#d73027")
colorLabels = c("2014-2015", "2015-2016", "2016-2017")

```

```{r}
seriesColor.labels = character()
seriesColor.values = character()
yearsAvailable = unique(wtemp.day$year.summer)

if (length(yearsAvailable)==0){
  ## no data available
  seriesColor.labels = c(seriesColor.labels, "SSTAARS Clim")
  seriesColor.values = c(seriesColor.values, "blue4")

  pp = ggplot()
  pp = pp + geom_line(data=climSSTAARS, aes(yDay.summer, TEMP, colour="SSTAARS Clim")) +
    annotate("text", x = 200, y = (Temp.scale.min + Temp.scale.max)/2, label = "NO WAVE BOUY DATA AVAILABLE FOR 2015-2017")
} else {
  pp = ggplot()
  ## add SSTAARS climatology
  pp = pp + geom_line(data=climSSTAARS, aes(yDay.summer, TEMP, colour="SSTAARS Clim"))
  seriesColor.labels = c(seriesColor.labels, "SSTAARS Clim")
  seriesColor.values = c(seriesColor.values, "blue4")

  ## add series
  if (2015 %in% yearsAvailable){
    pp = pp + geom_line(data = wtemp.day %>% filter(year.summer==2015), aes(yDay.summer, TEMP, colour="2014-2015"), size=1, alpha=0.7)
      seriesColor.labels = c(seriesColor.labels, "2015")
      seriesColor.values = c(seriesColor.values, "steelblue")
  }
  if (2016 %in% yearsAvailable){
    pp = pp + geom_line(data = wtemp.day %>% filter(year.summer==2016), aes(yDay.summer, TEMP, colour="2015-2016"), size=1, alpha=0.7)
    seriesColor.labels = c(seriesColor.labels, "2016")
    seriesColor.values = c(seriesColor.values, "#fc8d59")
  }
  if (2017 %in% yearsAvailable){
    pp = pp + geom_line(data = wtemp.day %>% filter(year.summer==2017), aes(yDay.summer, TEMP, colour="2016-2017"), size=1, alpha=0.7)
    seriesColor.labels = c(seriesColor.labels, "2017")
    seriesColor.values = c(seriesColor.values, "#d73027")
  }
}
## layout
pp = pp + labs(x="", y="Temperature °C") +
  ylim(Temp.scale.min, Temp.scale.max) +
  scale_color_manual(values = rev(seriesColor.values),
                     labels = rev(seriesColor.labels), aesthetics = "color") +
  theme_pubclean() +
  theme(legend.title = element_blank())
pp = ggplotly(pp)
pp = tidyPlotly(pp)
pp

```



Row
----------------------------------------

### Comments

The time series corresponding to 2015, 2016 and 2017, when available, are plotted in its climatological year, starting at October 1st of the previous year and ending September 30 of its year. For example, the 2016 time series starts at 2015-10-01 and ends 2016-09-30.

The default climatology is the one extracted for the site's coordinates from the SST Atlas of Australian Regional Seas (SSTAARS) (see [Wijffels et al. 2018](http://epubs.aims.gov.au/handle/11068/14860)), at a spatial resolution of ~2km.

The maximun temperature reported in the value Box is the maximum value of the 95% percentile of the day. This quantile avoids the effect of over-heating due to an occasional exposure to the air.








TIME SERIES
=========================================

Row
-----------------------------------------

### `r globalMD$SITE`

```{r}

fig = plot_ly(x=~wtemp.hour$dateTime, y=~wtemp.hour$TEMP, mode='lines', type="scatter",
              line = list(color = "coral"), name = "Hourly") %>%
  add_trace(x = ~wtemp.day$dateTime, y= ~wtemp.day$TEMP, type="scatter", mode="lines",
            line = list(color = "red"), name = "Day mean") %>%
  layout(
    title = "",
    xaxis = list(
      title="",
      rangeselector = list(
        buttons = list(
          list(
            count = 3,
            label = "3 mo",
            step = "month",
            stepmode = "backward"),
          list(
            count = 6,
            label = "6 mo",
            step = "month",
            stepmode = "backward"),
          list(
            count = 1,
            label = "1 yr",
            step = "year",
            stepmode = "backward"),
          list(step = "all")))),
        yaxis = list(title = "Temperature (°C)")) %>%
  rangeslider(start=ymd(20161001), end = ymd(20170930))
fig = fig %>% config(fig, displaylogo = FALSE)

fig

```


Row
------------------------------------------------

#### Comentary

The time series represents all available records from **`r floor_date(globalMD$DATE_START, "day")`** to **`r floor_date(globalMD$DATE_END, "day")`**. Move the range slider at the bottom of the plot to select or zoom sections of the data. Click on the legend to hide/show any time series.

For more details about this data go to the [Queensland Government Wave Monitoring site](https://www.qld.gov.au/environment/coasts-waterways/beach/monitoring/waves-sites)

